The \dealii{} Library, Version 9.3

### 2021-06-18 9.3/paper.tex
Fix minor issues.

\author[17]{Konrad Simon}
  \affil[17]{Department of Mathematics /
  Center for Earth System Research and Sustainability (CEN),
  University of Hamburg, Grindelberg 5, 20144 Hamburg, Germany}

@@

\author[16]{David Wells}
\affil[16]{Department of Mathematics, University of North Carolina,
  Chapel Hill, NC 27516, USA.
  {\texttt{drwells@email.unc.edu}}}

@@

The source based installation of \dealii{} and it's many dependent libraries
can be done with the \candi{} script tool for various
Linux operating systems, within the Windows Subsystem Linux (WSL) and on OSX (experimental).
%
The general assumption is that a C, C++ and Fortran compiler and suitable MPI-compilers
for the base compilers as well as the corresponding development system packages are
available.

>>>>

\author[13]{Konrad Simon}
  \affil[13]{Department of Mathematics/Center for Earth System Research and Sustainability (CEN),
  University of Hamburg, Grindelberg 5, 20144 Hamburg, Germany}

@@

\author[14]{David Wells}
\affil[14]{Department of Mathematics, University of North Carolina,
  Chapel Hill, NC 27516, USA.
  {\texttt{drwells@email.unc.edu}}}

@@

The source based installation of \dealii{} and its many dependent libraries
can be done with the \candi{} script tool for various
Linux operating systems, within the Windows Subsystem Linux (WSL) and on OSX (experimental).
%
The general assumption is that a C, C++ and Fortran compiler and suitable MPI-compilers
for the base compilers as well as the corresponding development system packages are
available.
